\markboth{BIBLIOGRAFÍA}{BIBLIOGRAFÍA}
\addcontentsline{toc}{chapter}{Bibliografía}

\begin{thebibliography}{99}

\bibitem{lewis2020rag}
P. Lewis, E. Perez, A. Piktus, F. Petroni, V. Karpukhin, N. Goyal,
H. Küttler, M. Lewis, W. Yih, T. Rocktäschel, S. Riedel y D. Kiela.
``Retrieval-Augmented Generation for Knowledge-Intensive NLP Tasks''.
NeurIPS, 2020. \url{https://arxiv.org/abs/2005.11401}.

\bibitem{wilson2019modeling}
R. C. Wilson y A. G. E. Collins.
``Ten simple rules for the computational modeling of behavioral data''.
{\it eLife}, 8:e49547, 2019.
\url{https://doi.org/10.7554/eLife.49547}.

\bibitem{sutton2018rl}
R. S. Sutton y A. G. Barto.
{\it Reinforcement Learning: An Introduction}. 2nd edition.
MIT Press, 2018. \url{http://incompleteideas.net/book/the-book-2nd.html}.

\bibitem{kahneman1979prospect}
D. Kahneman y A. Tversky.
``Prospect Theory: An Analysis of Decision under Risk''.
{\it Econometrica}, 47(2), 263--291, 1979.
\url{https://doi.org/10.2307/1914185}.

\bibitem{simon1955behavioral}
H. A. Simon. ``A Behavioral Model of Rational Choice''.
{\it The Quarterly Journal of Economics}, 69(1), 99--118, 1955.
\url{https://doi.org/10.2307/1884852}.

\bibitem{ratcliff1978theory}
R. Ratcliff. ``A theory of memory retrieval''.
{\it Psychological Review}, 85(2), 59--108, 1978.
\url{https://doi.org/10.1037/0033-295X.85.2.59}.

\bibitem{berthoud2011metabolic}
H.-R. Berthoud. ``Metabolic and hedonic drives in the neural control of
appetite: who is the boss?''. {\it Current Opinion in Neurobiology},
21(6), 888--896, 2011.
\url{https://doi.org/10.1016/j.conb.2011.09.004}.

\bibitem{karpukhin2020dpr}
V. Karpukhin, B. Oguz, S. Min, P. Lewis, L. Wu, S. Edunov, D. Chen y
W. Yih. ``Dense Passage Retrieval for Open-Domain Question Answering''.
EMNLP, 2020. \url{https://arxiv.org/abs/2004.04906}.

\bibitem{robertson2009bm25}
S. E. Robertson y H. Zaragoza. ``The Probabilistic Relevance Framework:
BM25 and Beyond''. {\it Foundations and Trends in Information Retrieval},
3(4), 333--389, 2009. \url{https://doi.org/10.1561/1500000019}.

\bibitem{cormack2009rrf}
G. V. Cormack, C. L. A. Clarke y S. Buettcher. ``Reciprocal rank fusion
outperforms condorcet and individual rank learning methods''. SIGIR, 2009.
\url{https://doi.org/10.1145/1571941.1572114}.

\bibitem{yan2024crag}
S. Yan, J. Gu, Y. Zhu y Z. Ling. ``Corrective Retrieval Augmented
Generation''. 2024. \url{https://arxiv.org/abs/2401.15884}.

\bibitem{hogan2021knowledgegraphs}
A. Hogan, E. Blomqvist, M. Cochez, C. d'Amato, G. de Melo, C. Gutiérrez
et al. ``Knowledge Graphs''. {\it ACM Computing Surveys}, 54(4), 2021.
\url{https://arxiv.org/abs/2003.02320}.

\bibitem{edge2024graphrag}
D. Edge, H. Trinh, N. Cheng, J. Bradley, A. Chao, A. Mody, S. Truitt,
D. Metropolitansky, R. O. Ness y J. Larson. ``From Local to Global: A
Graph RAG Approach to Query-Focused Summarization''. 2024.
\url{https://arxiv.org/abs/2404.16130}.

\bibitem{gutierrez2024hipporag}
B. Jiménez Gutiérrez, Y. Shu, Y. Gu, M. Yasunaga y Y. Su. ``HippoRAG:
Neurobiologically Inspired Long-Term Memory for Large Language Models''.
NeurIPS, 2024. \url{https://arxiv.org/abs/2405.14831}.

\bibitem{haveliwala2002topicsensitive}
T. H. Haveliwala. ``Topic-sensitive PageRank''. WWW, 517--526, 2002.
\url{https://doi.org/10.1145/511446.511513}.

\bibitem{park2023generativeagents}
J. S. Park, J. C. O'Brien, C. J. Cai, M. R. Morris, P. Liang y
M. S. Bernstein. ``Generative Agents: Interactive Simulacra of Human
Behavior''. 2023. \url{https://arxiv.org/abs/2304.03442}.

\bibitem{zhong2023memorybank}
W. Zhong, L. Guo, Q. Gao, H. Ye y Y. Wang. ``MemoryBank: Enhancing Large
Language Models with Long-Term Memory''. 2023.
\url{https://arxiv.org/abs/2305.10250}.

\bibitem{packer2023memgpt}
C. Packer, S. Wooders, K. Lin, V. Fang, S. G. Patil, I. Stoica y
J. E. Gonzalez. ``MemGPT: Towards LLMs as Operating Systems''. 2023.
\url{https://arxiv.org/abs/2310.08560}.

\bibitem{yao2023react}
S. Yao, J. Zhao, D. Yu, N. Du, I. Shafran, K. Narasimhan y Y. Cao.
``ReAct: Synergizing Reasoning and Acting in Language Models''. ICLR,
2023. \url{https://arxiv.org/abs/2210.03629}.

\bibitem{schick2023toolformer}
T. Schick, J. Dwivedi-Yu, R. Dessì, R. Raileanu, M. Lomeli, L. Zettlemoyer,
N. Cancedda y T. Scialom. ``Toolformer: Language Models Can Teach
Themselves to Use Tools''. 2023. \url{https://arxiv.org/abs/2302.04761}.

\bibitem{wu2023autogen}
Q. Wu, G. Bansal, J. Zhang, Y. Wu, B. Li, E. Zhu, L. Jiang et al.
``AutoGen: Enabling Next-Gen LLM Applications via Multi-Agent Conversation''.
2023. \url{https://arxiv.org/abs/2308.08155}.

\bibitem{qian2024chatdev}
C. Qian, W. Liu, H. Liu, N. Chen, Y. Dang, J. Li, C. Yang et al.
``ChatDev: Communicative Agents for Software Development''. ACL, 2024.
\url{https://arxiv.org/abs/2307.07924}.

\bibitem{yang2024sweagent}
J. Yang, C. E. Jimenez, A. Wettig, K. Lieret, S. Yao, K. Narasimhan y
O. Press. ``SWE-agent: Agent-Computer Interfaces Enable Automated Software
Engineering''. 2024. \url{https://arxiv.org/abs/2405.15793}.

\bibitem{chen2021codex}
M. Chen, J. Tworek, H. Jun, Q. Yuan, H. P. de Oliveira Pinto, J. Kaplan
et al. ``Evaluating Large Language Models Trained on Code''. 2021.
\url{https://arxiv.org/abs/2107.03374}.

\bibitem{austin2021programsynthesis}
J. Austin, A. Odena, M. Nye, M. Bosma, H. Michalewski, D. Dohan,
E. Jiang et al. ``Program Synthesis with Large Language Models''. 2021.
\url{https://arxiv.org/abs/2108.07732}.

\bibitem{scholak2021picard}
T. Scholak, N. Schucher y D. Bahdanau. ``PICARD: Parsing Incrementally for
Constrained Auto-Regressive Decoding from Language Models''. EMNLP, 2021.
\url{https://arxiv.org/abs/2109.05093}.

\bibitem{madaan2023selfrefine}
A. Madaan, N. Tandon, P. Gupta, S. Hallinan, L. Gao, S. Wiegreffe,
U. Alon et al. ``Self-Refine: Iterative Refinement with Self-Feedback''.
2023. \url{https://arxiv.org/abs/2303.17651}.

\bibitem{shinn2023reflexion}
N. Shinn, F. Cassano, E. Berman, A. Gopinath, K. Narasimhan y S. Yao.
``Reflexion: Language Agents with Verbal Reinforcement Learning''. 2023.
\url{https://arxiv.org/abs/2303.11366}.

\bibitem{pazos2026agrex}
P. Pazos Parada. {\it Agrex: real-time graph visualizer for AI agent execution
flows}. Software open source, 2026. Visor:
\url{https://agrex.ppazosp.dev}. Paquete npm:
\url{https://www.npmjs.com/package/@ppazosp/agrex}.

\end{thebibliography}
