\markboth{BIBLIOGRAFÍA}{BIBLIOGRAFÍA}
\addcontentsline{toc}{chapter}{Bibliografía}

\begin{thebibliography}{99}

\bibitem{lewis2020rag}
P. Lewis, E. Perez, A. Piktus, F. Petroni, V. Karpukhin, N. Goyal, et al.,
``Retrieval-augmented generation for knowledge-intensive NLP tasks,'' in
\emph{Proc. Adv. Neural Inf. Process. Syst. (NeurIPS)}, 2020. Accessed:
Jun. 2026. [Online]. Available: \url{https://arxiv.org/abs/2005.11401}

\bibitem{karpukhin2020dpr}
V. Karpukhin, B. Oguz, S. Min, P. Lewis, L. Wu, S. Edunov, et al., ``Dense
passage retrieval for open-domain question answering,'' in \emph{Proc. Conf.
Empirical Methods Natural Lang. Process. (EMNLP)}, 2020. Accessed: Jun. 2026.
[Online]. Available: \url{https://arxiv.org/abs/2004.04906}

\bibitem{robertson2009bm25}
S. E. Robertson and H. Zaragoza, ``The probabilistic relevance framework:
BM25 and beyond,'' \emph{Found. Trends Inf. Retr.}, vol.~3, no.~4,
pp.~333--389, 2009. Accessed: Jun. 2026. [Online]. Available:
\url{https://doi.org/10.1561/1500000019}

\bibitem{gutierrez2024hipporag}
B. Jiménez Gutiérrez, Y. Shu, Y. Gu, M. Yasunaga, and Y. Su, ``HippoRAG:
Neurobiologically inspired long-term memory for large language models,'' in
\emph{Proc. Adv. Neural Inf. Process. Syst. (NeurIPS)}, 2024. Accessed:
Jun. 2026. [Online]. Available: \url{https://arxiv.org/abs/2405.14831}

\bibitem{edge2024graphrag}
D. Edge, H. Trinh, N. Cheng, J. Bradley, A. Chao, A. Mody, et al., ``From
local to global: A graph RAG approach to query-focused summarization,''
arXiv:2404.16130, 2024. Accessed: Jun. 2026. [Online]. Available:
\url{https://arxiv.org/abs/2404.16130}

\bibitem{hogan2021knowledgegraphs}
A. Hogan, E. Blomqvist, M. Cochez, C. d'Amato, G. de Melo, C. Gutiérrez,
et al., ``Knowledge graphs,'' \emph{ACM Comput. Surv.}, vol.~54, no.~4,
art.~71, 2021. Accessed: Jun. 2026. [Online]. Available:
\url{https://arxiv.org/abs/2003.02320}

\bibitem{park2023generativeagents}
J. S. Park, J. C. O'Brien, C. J. Cai, M. R. Morris, P. Liang, and
M. S. Bernstein, ``Generative agents: Interactive simulacra of human
behavior,'' in \emph{Proc. 36th Annu. ACM Symp. User Interface Software
and Technology (UIST)}, 2023. Accessed: Jun. 2026. [Online].
Available: \url{https://doi.org/10.1145/3586183.3606763}

\bibitem{hong2024metagpt}
S. Hong, X. Zheng, J. Chen, Y. Cheng, J. Wang, C. Zhang, et al.,
``MetaGPT: Meta programming for a multi-agent collaborative framework,'' in
\emph{Proc. Int. Conf. Learn. Represent. (ICLR)}, 2024. Accessed:
Jun. 2026. [Online]. Available:
\url{https://openreview.net/forum?id=VtmBAGCN7o}

\bibitem{guo2024llmbased}
T. Guo, X. Chen, Y. Wang, R. Chang, S. Pei, N. V. Chawla, et al., ``Large
language model based multi-agents: A survey of progress and challenges,'' in
\emph{Proc. Int. Joint Conf. Artif. Intell. (IJCAI)}, 2024,
pp.~8048--8057. Accessed: Jun. 2026. [Online]. Available:
\url{https://www.ijcai.org/proceedings/2024/0890.pdf}

\bibitem{yao2023react}
S. Yao, J. Zhao, D. Yu, N. Du, I. Shafran, K. Narasimhan, et al.,
``ReAct: Synergizing reasoning and acting in language models,'' in
\emph{Proc. Int. Conf. Learn. Represent. (ICLR)}, 2023. Accessed:
Jun. 2026. [Online]. Available: \url{https://arxiv.org/abs/2210.03629}

\bibitem{schick2023toolformer}
T. Schick, J. Dwivedi-Yu, R. Dessì, R. Raileanu, M. Lomeli, L. Zettlemoyer,
et al., ``Toolformer: Language models can teach themselves to use tools,''
arXiv:2302.04761, 2023. Accessed: Jun. 2026. [Online]. Available:
\url{https://arxiv.org/abs/2302.04761}

\bibitem{madaan2023selfrefine}
A. Madaan, N. Tandon, P. Gupta, S. Hallinan, L. Gao, S. Wiegreffe, et al.,
``Self-refine: Iterative refinement with self-feedback,''
arXiv:2303.17651, 2023. Accessed: Jun. 2026. [Online]. Available:
\url{https://arxiv.org/abs/2303.17651}

\bibitem{shinn2023reflexion}
N. Shinn, F. Cassano, E. Berman, A. Gopinath, K. Narasimhan, and S. Yao,
``Reflexion: Language agents with verbal reinforcement learning,''
arXiv:2303.11366, 2023. Accessed: Jun. 2026. [Online]. Available:
\url{https://arxiv.org/abs/2303.11366}

\bibitem{chen2021codex}
M. Chen, J. Tworek, H. Jun, Q. Yuan, H. P. de Oliveira Pinto, J. Kaplan,
et al., ``Evaluating large language models trained on code,''
arXiv:2107.03374, 2021. Accessed: Jun. 2026. [Online]. Available:
\url{https://arxiv.org/abs/2107.03374}

\bibitem{austin2021programsynthesis}
J. Austin, A. Odena, M. Nye, M. Bosma, H. Michalewski, D. Dohan, et al.,
``Program synthesis with large language models,'' arXiv:2108.07732,
2021. Accessed: Jun. 2026. [Online]. Available:
\url{https://arxiv.org/abs/2108.07732}

\bibitem{jimenez2024swebench}
C. E. Jimenez, J. Yang, A. Wettig, S. Yao, K. Pei, O. Press, et al.,
``SWE-bench: Can language models resolve real-world GitHub issues?,'' in
\emph{Proc. Int. Conf. Learn. Represent. (ICLR)}, 2024. Accessed:
Jun. 2026. [Online]. Available:
\url{https://openreview.net/forum?id=VTF8yNQM66}

\bibitem{yang2024sweagent}
J. Yang, C. E. Jimenez, A. Wettig, K. Lieret, S. Yao, K. Narasimhan, et al.,
``SWE-agent: Agent-computer interfaces enable automated software
engineering,'' arXiv:2405.15793, 2024. Accessed: Jun. 2026. [Online].
Available: \url{https://arxiv.org/abs/2405.15793}

\bibitem{qian2024chatdev}
C. Qian, W. Liu, H. Liu, N. Chen, Y. Dang, J. Li, et al., ``ChatDev:
Communicative agents for software development,'' in \emph{Proc. Annu.
Meeting Assoc. Comput. Linguist. (ACL)}, 2024. Accessed: Jun. 2026.
[Online]. Available: \url{https://arxiv.org/abs/2307.07924}

\bibitem{peng2023impact}
S. Peng, E. Kalliamvakou, P. Cihon, and M. Demirer, ``The impact of AI on
developer productivity: Evidence from GitHub Copilot,'' arXiv:2302.06590,
2023. Accessed: Jun. 2026. [Online]. Available:
\url{https://arxiv.org/abs/2302.06590}

\bibitem{cui2025effects}
Z. Cui, M. Demirer, S. Jaffe, L. Musolff, S. Peng, and T. Salz, ``The
effects of generative AI on high-skilled work: Evidence from three field
experiments with software developers,'' \emph{Manage. Sci.}, 2026.
Accessed: Jun. 2026. [Online]. Available:
\url{https://doi.org/10.1287/mnsc.2025.00535}

\bibitem{butler2024dear}
J. Butler, J. Suh, S. Haniyur, and C. Hadley, ``Dear diary: A randomized
controlled trial of generative AI coding tools in the workplace,'' in
\emph{Proc. IEEE/ACM Int. Conf. Softw. Eng., Softw. Eng. Pract.
(ICSE-SEIP)}, 2025. Accessed: Jun. 2026. [Online]. Available:
\url{https://arxiv.org/abs/2410.18334}

\bibitem{sutton2018rl}
R. S. Sutton and A. G. Barto, \emph{Reinforcement Learning: An
Introduction}, 2nd ed. Cambridge, MA, USA: MIT Press, 2018.

\bibitem{epstein1999abm}
J. M. Epstein, ``Agent-based computational models and generative social
science,'' \emph{Complexity}, vol.~4, no.~5, pp.~41--60, 1999. Accessed:
Jun. 2026. [Online]. Available:
\url{https://doi.org/10.1002/(SICI)1099-0526(199905/06)4:5<41::AID-CPLX9>3.0.CO;2-F}

\bibitem{railsback2019abm}
S. F. Railsback and V. Grimm, \emph{Agent-Based and Individual-Based
Modeling: A Practical Introduction}, 2nd ed. Princeton, NJ, USA:
Princeton University Press, 2019.

\bibitem{banks2010simulation}
J. Banks, J. S. Carson, B. L. Nelson, and D. M. Nicol,
\emph{Discrete-Event System Simulation}, 5th ed. Upper Saddle River, NJ,
USA: Prentice Hall, 2010.

\bibitem{sargent2013vv}
R. G. Sargent, ``Verification and validation of simulation models,''
\emph{Journal of Simulation}, vol.~7, no.~1, pp.~12--24, 2013. Accessed:
Jun. 2026. [Online]. Available: \url{https://doi.org/10.1057/jos.2012.20}

\bibitem{artificialanalysis2026index}
Artificial Analysis, ``Artificial Analysis Intelligence Index,'' 2026.
Accessed: Jun. 2026. [Online]. Available:
\url{https://artificialanalysis.ai/evaluations/artificial-analysis-intelligence-index}

\bibitem{lmarena2026webdev}
Arena.ai, ``Code Arena: WebDev Overall,'' 2026. Accessed: Jun. 2026.
[Online]. Available: \url{https://arena.ai/leaderboard/code/webdev}

\bibitem{mohammadi2025agenteval}
M. Mohammadi, J. Li, K. K. Lo, and W. T. Yip, ``Evaluation of large language
model--based agents: A survey,'' in \emph{Proc. 31st ACM SIGKDD Conf. Knowl.
Discovery Data Mining (KDD)}, 2025. Accessed: Jun. 2026. [Online]. Available:
\url{https://doi.org/10.1145/3711896.3736570}

\bibitem{zheng2023judge}
L. Zheng, W.-L. Chiang, Y. Sheng, S. Zhuang, Z. Wu, Y. Zhuang, et al.,
``Judging LLM-as-a-judge with MT-Bench and Chatbot Arena,'' in \emph{Proc.
Adv. Neural Inf. Process. Syst. (NeurIPS)}, 2023. Accessed: Jun. 2026.
[Online]. Available: \url{https://arxiv.org/abs/2306.05685}

\bibitem{li2024judges}
H. Li, Q. Dong, J. Chen, H. Su, Y. Zhou, Q. Ai, et al., ``LLMs-as-judges: A
comprehensive survey on LLM-based evaluation methods,'' arXiv:2412.05579,
2024. Accessed: Jun. 2026. [Online]. Available:
\url{https://arxiv.org/abs/2412.05579}

\bibitem{calm2024biases}
J. Ye, Y. Wang, Y. Huang, D. Chen, Q. Zhang, N. Moniz, et al., ``Justice or
prejudice? Quantifying biases in LLM-as-a-judge,'' arXiv:2410.02736, 2024.
Accessed: Jun. 2026. [Online]. Available:
\url{https://arxiv.org/abs/2410.02736}

\bibitem{wilson2019tenrules}
R. C. Wilson and A. G. E. Collins, ``Ten simple rules for the computational
modeling of behavioral data,'' \emph{eLife}, vol.~8, art.~e49547, 2019.
Accessed: Jun. 2026. [Online]. Available:
\url{https://doi.org/10.7554/eLife.49547}

\bibitem{palminteri2017falsification}
S. Palminteri, V. Wyart, and E. Koechlin, ``The importance of falsification in
computational cognitive modeling,'' \emph{Trends Cogn. Sci.}, vol.~21, no.~6,
pp.~425--433, 2017. Accessed: Jun. 2026. [Online]. Available:
\url{https://doi.org/10.1016/j.tics.2017.03.011}

\bibitem{wang2020qags}
A. Wang, K. Cho, and M. Lewis, ``Asking and answering questions to evaluate
the factual consistency of summaries,'' in \emph{Proc. 58th Annu. Meeting
Assoc. Comput. Linguistics (ACL)}, 2020. Accessed: Jun. 2026. [Online].
Available: \url{https://aclanthology.org/2020.acl-main.450/}

\bibitem{laban2022summac}
P. Laban, T. Schnabel, P. N. Bennett, and M. A. Hearst, ``SummaC: Re-visiting
NLI-based models for inconsistency detection in summarization,'' \emph{Trans.
Assoc. Comput. Linguistics (TACL)}, vol.~10, pp.~163--177, 2022. Accessed:
Jun. 2026. [Online]. Available: \url{https://aclanthology.org/2022.tacl-1.10/}

\bibitem{charnov1976mvt}
E. L. Charnov, ``Optimal foraging, the marginal value theorem,'' \emph{Theor.
Population Biol.}, vol.~9, no.~2, pp.~129--136, 1976. Accessed: Jun. 2026.
[Online]. Available: \url{https://doi.org/10.1016/0040-5809(76)90040-X}

\bibitem{macarthur1966dietbreadth}
R. H. MacArthur and E. R. Pianka, ``On optimal use of a patchy environment,''
\emph{Amer. Naturalist}, vol.~100, no.~916, pp.~603--609, 1966. Accessed:
Jun. 2026. [Online]. Available: \url{https://doi.org/10.1086/282454}

\end{thebibliography}
